\chapter{Conclusion}
\section{Final Thoughts}
Overall, I had a very positive experience during my time at HubSpot. This internship was really useful and it taught me a bunch of skills and given me opportunities I would never have gotten during a college semester or in a college semester. \newline \\ I was lucky to be placed alongside a group of really intelligent and experienced engineers that I could learn a lot from. The new tools and technology that I encountered during my time at HubSpot, whilst some are in-house, are invaluable and I think they'll be very useful to have when anywhere in the industry. The internship allowed me to gain plenty of experience in numerous aspects of the software engineering process, from the different areas of agile methodology to using continuous integration software. \newline \\ In terms of soft skills, I learnt a lot about how to work in a professional capacity from working alongside my team mates and how to collaborate and interact with people. My team didn't treat me as 'just an intern' but instead treated me as a full time member of the team and encouraged me to engage in conversations about how the team should move forward. The weekly meetings with my team lead really helped me to grow and develop as an engineer and helped me grow my confidence overall. \newline \\  The actual project work that I worked on during my time at HubSpot was very interesting and I learnt a lot about how code is written in a professional environment and how important it is to write clean, maintainable code. While the entire project couldn't be completed during my time there, I'm happy to know my addition to the team is something that will affect customers positively and will have a lasting impact long after I have left. 